BurgerTown Presents: Open Adcess

### 2017-04-19 paper-sponsorships.tex
updated notion of scientific truth

Several ``bloggers" have deigned to argue that this arrangement gives particular corporations undue influence over science and could lead to corruption. These agitators are, of course, anti-science zealots who fail to realize the emancipatory potential of this settlement system. Much as the visionary rulings of Anthony Kennedy and others have opened up our politics to make it more responsive to democratic speech, ISDS will make science more responsive to the needs of democratic actors, like 501(c)(4) ``social welfare" nonprofits. Welfare! It will democratize our understanding of reality, taking science out of the smooth, mildly scented ivory tower and cramming it into the ad-plastered public square. Science is agoraphobic but its future is in the agora of the brainscape---the marketplace of ideas---so (to coin a term) ISDS is the deagoraphobification of science. Science cannot ignore society. Science must come to where the flavor is.

>>>>

Several ``bloggers" and fuddy-duddies fixated on a staid notion of ``truth" (lacking the agility and dynamism that characterize a proactive, change-driven science) have deigned to argue that this arrangement gives particular corporations undue influence over science and could lead to corruption. These agitators are, of course, anti-science zealots who fail to realize the emancipatory potential of this settlement system. Much as the visionary rulings of Anthony Kennedy and others have opened up our politics to make it more responsive to democratic speech, ISDS will make science more responsive to the needs of democratic actors, like 501(c)(4) ``social welfare" nonprofits. Welfare! It will democratize our understanding of reality, taking science out of the smooth, mildly scented ivory tower and cramming it into the ad-plastered public square. Science is agoraphobic but its future is in the agora of the brainscape---the marketplace of ideas---so (to coin a term) ISDS is the deagoraphobification of science. Science cannot ignore society. Science must come to where the flavor is.
